survey-analysis-final

### 2021-01-28 4_Result.tex
revisao da secao com resultados do survey

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants. Figure~\ref{fig:degree} and Figure~\ref{fig:xp} show the distributions of the subjects,
according to their education level and years of programming experience, respectively.

\begin{figure}[htb]
      \centering
      \includegraphics[width=\columnwidth]{images/dem-education-1.pdf}
      \caption{Participants' Education Level}\label{fig:degree}
  \end{figure}

  \begin{figure}[htb]
      \centering
      \includegraphics[width=\columnwidth]{images/dem-experience-1.pdf}
      \caption{Participants' Experience} \label{fig:xp}
  \end{figure}

Figure~\ref{fig:xp} shows that more than a half of the participants hold either a BS degree or had taken some university course, meaning the participants have had some level of formal education on programming. No subject reported to have never attended university. Our audience comprises skillful developers, and 93\% of the respondents have more than one year of experience with programming (see Figure~\ref{fig:xp}). Actually, 56\% of the participants have either between four and ten years of experience (37\%) or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience. In this way, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experience developers.

@@

Each participant in this study evaluated {\color{red}10} code snippets, from which 5 were in their confusing versions, whilst the other 5 contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. We collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). Our final dataset consists of 70 complete Latin Squares.

Regarding \emph{correctness}, Table~\ref{results_correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey. Accordingly, the version of seven code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, \emph{Comma Operator} atom presents the highest impact on misunderstanding. 
Curiously, frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.

Moreover, as the boxplot in Figure \ref{fig:boxplotcorrectness} shows, there is a considerable decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of answers where there was no atoms had almost no dispersion, which is a sign that the non-confusing code is easier to evaluate correctly.

@@

\begin{table*}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{tabular}{lccc|c} \toprule
 % & \multicolumn{2}{c}{Total Number of Correct Answers} & \\ [0.1cm]
  Atom & Confuse Code & Clean Code & $\Delta$(\%) & Effect Size (Odds Ratio) \\ \midrule
  Comma Operator &  28 &  65 & +132 & 19.02 \\ 
  {\color{red}Automatic Semicolon Insertion} &  32 &  68 & +112 & 39.32 \\ 
  Post Increment &  48 &  64 & +33 & 4.83 \\ 
  Ommitted Curly Braces &  47 &  58 &  +23 & 2.35 \\
  Assignment as Value &  56 &  68 &  +21 & 8.38 \\ 
  Implict Predicate &  58 &  68 &  +17 & 6.94 \\ 
  Logic as Control Flow &  41 &  48 &  +17 & 1.53 \\ 
  Ternary Operator &  60 &  66 &  +10 & 2.73 \\ 
  Pre Increment &  50 &  53 &  +6 & 1.24 \\ 
  Arithmetic as Logic &  64 &  63 &  -2 & 0.84 \\ \bottomrule 
\end{tabular}
}
\end{table*}

@@

\rb{verificar a consistencia nas questoes de pesquisa mais especificas}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confuse and clean code). The result shows that the confusing version of the code snippets impacts code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact on correctness. Although the results suggest that experience impact correctness, the education level does not. We then replicate the \emph{Pearson's Chi-squared test} for each experience group (see Figure~\ref{fig:xp}) and found that the statistic difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre Increment. Nonetheless, for the remaining candidates, the effect size is considerable. For instance, the Comma Operators leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confuse version of the code snippet.

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants give a correct answer about the expected outcomes of a code snippet, considering both confuse and clean versions. Eight atom candidates require an increasing cognitive workload. For these eight atom candidates, developers take at least 5.90\% less time on average to find a correct answer---when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, take less time to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, there was an increase
of 29.06\% and 38.19\% in the average time taken to give a correct answwer---wherein the clean code versions.

\begin{table*}[htbp]
\caption{Time in seconds to submit a {\color{red}correct} answer}
\label{tab:difference-time-taken}
\centering{
\begin{tabular}{lccc|cc} \toprule
Atom & Confuse Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
{\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
Ommitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
Implict Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
Pre Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
         \bottomrule
    \end{tabular}}
\end{table*}

\subsubsection*{Hypotheis Testing}
We use the non-parametric \emph{Mann-Whitney test} to
investigates the null hypothesis that developers 
spend the same ammount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confuse or the clean version
of the code. Table~\ref{tab:difference-time-taken}
shows the results, which suggest that we
should refute the null hypothes for
five atom candidates (Comma Operator, Logic
as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre Increment). For the first three,
the analysis suggest that the participants
need more time to predict the outcome of
the code snippet in the confuse code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre Increment, the participants take less time
to predict the outcome of the code snippets in
the confuse version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre Increment.

\rb{Acho que dever\'{i}mos justificar o uso do Cliff's Delta aqui e o Odds Ratio na
  se\c c\~{a}o anterior.}

\subsection{Discussion}

\rb{Acho que podemos incluir uma discuss\~{a}o ao
  t\'{e}ermino de cada uma das se\c c\~{o}es com
  resultados. Ou separamos em uma \'{u}nica
se\c c\~{a}o de discuss\~{a}o?}

@@

\rb{acho que essa separa\c c\~{a}o em dois rounds est\'{a}
  gerando uma complexidade desnecess\'{a}ria. vou tentar
  remover isso}.

@@

\subsubsection*{Participants views of the atoms} Interesting,
only for the \emph{ternary operator} scenario the participants
prefer the version of the code with the atom of confusion,
instead of the more cleaner version without the atom of confusion.
Even in this case, some participants who opted for
the \emph{left-hand-side} (with the atom of confusion) version
still believed that the \emph{right-hand-side} (without the atom of
confusion) version was more readable (see Figure~\ref{code:ternary}). 
The following quotes were extracted from the transcripts with
three inteviwes:

@@

The atom candidate Ternary Operator also opens up
the possibility for a derivative construct that JavaScript
allows which can be rather confusing, and that is the nested
ternaries construct, in which the right-hand side of the a
ternary operator can be another ternary construct.
While nested ternaries remove the number of lines that
would be necessary to construct using nested if-then-else statements,
they can become quite taxing, cognitively speaking, to understand.
Therefore, nested ternaries are a choice of atoms to be analysed in future work.

@@

  \hline
Atom & Projects & Ocurrences/KLOC & Category \\ 
 \hline
Ternary Operator & 100\% & 10.16 &  highly used \\ 
  Access Property & 100\% & 3.63 &  highly used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 &  highly used \\ 
  Post Increment & 90.28\% & 5.62 &  highly used \\ 
  Arrow Function & 83.33\% & 21.10 &  highly used \\ 
  Change Literal Encoding & 76.39\% & 21.43 &  highly used \\ 
  Object Destructing & 72.22\% & 2.86 &  highly used \\ 
  Pre-Increment & 83.33\% & 1.04 & commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 & commonly used \\ 
  Implicit Operand Conversion & 79.17\% & 0.80 & commonly used \\ 
  Array Destructing & 62.50\% & 0.47 & commonly used \\ 
  Array Spread & 59.72\% & 0.31 & commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 & commonly used \\ 
  Object Spread & 55.56\% & 0.64 & commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 & little used \\ 
  Comma Operator & 15.28\% & 0.03 & little used \\ 
   \hline
\end{tabular}
\end{table}

>>>>

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants (in a total of 70 replicas).
All participants had taken at least some university course or hold a bachelor
degree or equivalent, meaning the participants have had some
level of formal education on programming.
Twenty four participants hold either a master degree (21 participants) or a doctorate degree (3 participant).

%% Figure~\ref{fig:degree} and Figure~\ref{fig:xp} show the distributions of the subjects,
%% according to their education level and years of programming experience, respectively.

%% \begin{figure}[htb]
%%       \centering
%%       \includegraphics[width=\columnwidth]{images/dem-education-1.pdf}
%%       \caption{Participants' Education Level}\label{fig:degree}
%%   \end{figure}

%%   \begin{figure}[htb]
%%       \centering
%%       \includegraphics[width=\columnwidth]{images/dem-experience-1.pdf}
%%       \caption{Participants' Experience} \label{fig:xp}
%%   \end{figure}
%Figure~\ref{fig:xp} shows that more than a half of

Our audience comprises professional developers,
and 93\% of the respondents have more than one year of experience with programming.
% (see Figure~\ref{fig:xp}). 
Actually, 56\% of the participants have either between four and ten years of experience (37\%)
or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience.
Accordingly, we characterize the effect of atoms of confusion in JavaScript
code taking into account the perceptions of both novice and experience developers.

@@

Each participant in this study evaluated 10 code snippets, from which 5 were in their confusing versions, whilst the other 5 contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness. Accordingly, the version of six code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, the presence of the \emph{Comma Operator} atom presents the highest impact on
misunderstanding, and  
frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.
The boxplot of Figure~\ref{fig:boxplotcorrectness} shows a nonnegligible decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of responses with no atoms had almost no dispersion, which signifies that the non-confusing code is easier to evaluate correctly.

@@

\begin{table*}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{tabular}{lccc|c} \toprule
 % & \multicolumn{2}{c}{Total Number of Correct Answers} & \\ [0.1cm]
  Atom & Confuse Code & Clean Code & $\Delta$(\%) & Effect Size (Odds Ratio) \\ \midrule
  Comma Operator &  28 &  65 & +132 & 19.02 \\ 
%   {\color{red}Automatic Semicolon Insertion} &  32 &  68 & +112 & 39.32 \\ 
  Post Increment &  48 &  64 & +33 & 4.83 \\ 
  Omitted Curly Braces &  47 &  58 &  +23 & 2.35 \\
  Assignment as Value &  56 &  68 &  +21 & 8.38 \\ 
  Implicit Predicate &  58 &  68 &  +17 & 6.94 \\ 
  Logic as Control Flow &  41 &  48 &  +17 & 1.53 \\ 
  Ternary Operator &  60 &  66 &  +10 & 2.73 \\ 
  Pre Increment &  50 &  53 &  +6 & 1.24 \\ 
  Arithmetic as Logic &  64 &  63 &  -2 & 0.84 \\ \bottomrule 
\end{tabular}
}
\end{table*}

@@

% \rb{verificar a consistencia nas questoes de pesquisa mais especificas}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confuse and clean code). The result indicates that the confusing version of the code snippets impacts code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact on correctness. Although the results suggest that experience impact correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistic difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see the Effect Size column of Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre Increment. Nonetheless, for the remaining candidates, the effect size is significant. For instance, the Comma Operator leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confuse version of the code snippet.

\begin{mh}
  The results of our exploratory data analysis and
  hypothesis testing suggest that the atom
  candidates Comma Operator, Post Increment,
  Omitted Curly Braces, Assignment as Value,
  Implicit Predicate, and Ternary Operator
  introduce some degree of misunderstanding
  in JavaScript code. 
\end{mh}

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants give a correct answer about the expected outcomes of a code snippet, considering both confuse and clean versions. Seven atom candidates require an increasing cognitive workload. For these seven atom candidates, developers take at least 5.90\% less time on average to find a correct answer---when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, take less time to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, there was an increase
of 29.06\% and 38.19\% in the average time taken to give a correct answer---wherein the clean code versions.

\begin{table*}[htbp]
\caption{Time in seconds to submit a {\color{red}correct} answer}
\label{tab:difference-time-taken}
\centering{
\begin{tabular}{lccc|cc} \toprule
Atom & Confuse Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
Pre Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
         \bottomrule
    \end{tabular}}
\end{table*}

\subsubsection*{Hypothesis Testing}
We use the non-parametric \emph{Mann-Whitney test} to
investigates the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confuse or the clean version
of the code. Table~\ref{tab:difference-time-taken}
shows the results, which suggest that we
should refute the null hypotheses for
five atom candidates (Comma Operator, Logic
as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre Increment). For the first three,
the analysis suggest that the participants
need more time to predict the outcome of
the code snippet in the confuse code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre Increment, the participants take less time
to predict the outcome of the code snippets in
the confuse version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre Increment.

\begin{mh}
  The results suggest that developers spend
  significantly more time to predict the
  correct answer in the presence of the
  atom candidates Comma Operator, Logic as
  Control Flow, and Implicit Predicate. Conversely,
  the version of the code snippets with the
  atom candidates Arithmetic as Logic and
  Pre Increment demands less time to
  predict the correct answers. 
\end{mh}

@@

%% \rb{acho que essa separa\c c\~{a}o em dois rounds est\'{a}
%%   gerando uma complexidade desnecess\'{a}ria. vou tentar
%%   remover isso}.

@@

\subsubsection*{Participants views of the atoms} Interesting,
only for the \emph{ternary operator} scenario the participants
prefer the version of the code with the atom of confusion,
instead of the more cleaner version without the atom of confusion.
Even in this case, some participants who opted for
the \emph{left-hand-side} (with the atom of confusion) version
still believed that the \emph{right-hand-side} (without the atom of
confusion) version was more readable (see Figure~\ref{code:ternary}). 
The following quotes were extracted from the transcripts with
three interviewees:

@@

The atom candidate Ternary Operator also opens up
the possibility for a derivative construct that JavaScript
allows which can be rather confusing, and that is the nested
ternaries construct, in which the right-hand side of the a
ternary operator can be another ternary construct.
While nested ternaries remove the number of lines that
would be necessary to construct using nested if-then-else statements,
they can become quite taxing, cognitively speaking, to understand.
Therefore, nested ternaries are a choice of atoms to be analyzed in future work.

@@

  \hline
Atom & Projects & Occurrences/KLOC & Category \\ 
 \hline
Ternary Operator & 100\% & 10.16 &  highly used \\ 
  Access Property & 100\% & 3.63 &  highly used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 &  highly used \\ 
  Post Increment & 90.28\% & 5.62 &  highly used \\ 
  Arrow Function & 83.33\% & 21.10 &  highly used \\ 
  Change Literal Encoding & 76.39\% & 21.43 &  highly used \\ 
  Object Destructing & 72.22\% & 2.86 &  highly used \\ 
  Pre-Increment & 83.33\% & 1.04 & commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 & commonly used \\ 
  Implicit Operand Conversion & 79.17\% & 0.80 & commonly used \\ 
  Array Destructing & 62.50\% & 0.47 & commonly used \\ 
  Array Spread & 59.72\% & 0.31 & commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 & commonly used \\ 
  Object Spread & 55.56\% & 0.64 & commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 & little used \\ 
  Comma Operator & 15.28\% & 0.03 & little used \\ 
   \hline
\end{tabular}
\end{table}

### 2021-01-28 dataset/survey-results-final.Rmd
incluindo alguns plots
revisao da secao com resultados do survey

---
title: "survey-analysis-final"
output: html_document
---

@@

barplot(demEducation$total, col=topo.colors(5), ylim = c(0, 70), cex=0.7, cex.lab = 0.7, cex.axis=0.7, ylab="Number of participants")

@@

chiTest <- c()
oddsRatio <- c()
mannWhitneyTest <- c()
cliffDelta <- c()

@@

  chiTest[i] <- format.pval(test$p.value) 
  oddsRatio[i] <- odds.ratio(tableCorrectness)$OR

@@

analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, mannWhitneyTest, cliffDelta)
analysis_df <- analysis_df[order(-oddsRatio),]

colnames(analysis_df) <- c("Atom", "ChiTest", "Odds Ratio Correctness", "Wilcox Test (Time)", "Cliff Delta")

>>>>

---
title: "survey-analysis-final"
output:
  pdf_document: default
  html_document: default
---

@@

demEducation
barplot(demEducation$total, col=topo.colors(5), ylim = c(0, 70), cex=0.7, cex.lab = 0.7, cex.axis=0.7, ylab="Number of participants")

@@

chiTest <- c()
oddsRatio <- c()
oddsRatioTest <- c()
mannWhitneyTest <- c()
cliffDelta <- c()

@@

  chiTest[i] <- format.pval(test$p.value) 
  oddsRatio[i] <- odds.ratio(tableCorrectness)$OR
  oddsRatioTest[i] <- format.pval(odds.ratio(tableCorrectness)$p)

@@

analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, oddsRatioTest, mannWhitneyTest, cliffDelta)
analysis_df <- analysis_df[order(-oddsRatio),]

colnames(analysis_df) <- c("Atom", "ChiTest", "Odds Ratio Correctness", "p-value", "Wilcox Test (Time)", "Cliff Delta")
